The paper on \Large \bf Blockchain Frontrunning

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] revisions on Intro

The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started. Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, would run in front of the others to get their orders in before the change in the market to profit from the change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However with the rapid advances of the technology in the last few decades, trading is not done in person anymore and new generation front-running was feasible through high speed networks. Furthermore, Blockchain technology has introduced transparency and open markets which led to a new era of front-running and it inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that had been linked to front-running attacks on blockchain. We started by looking at one specific case of front-running on Ethereum blockchain, However, the goal of this paper is to provide a complete look at the front-running issues. %and thus the aforementioned will remain out of the scope of this research study.
There has been little quantitative analysis and research of the front-running issue in decentralized applications, we aim to take a thorough look into the history of the front-running, discuss multiple existing issues in the eco-system and systematize the proposed solutions, and eventually match these solutions to their suitable use cases. \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention". }

% PAPER BEING SOLD HERE
%\textbf{Note to Change the structure of the paper: to pitch this paper as a case study, we can polish it as a status,im ico case study: 1) here is the status.im ico project that we look at 2) we find that the issue is mostly the frontrunning 3) So we take a deep look into what is frontrunning 4) we find other case studies that are vulnerable and go through each case}

%Decentral applications are on the rise with Turing complete blockchains maturing to handle high monetary value transactions. Tokenization mushroomed to a whole ecosystem of tokenized applications on the blockchain, these applications inherently become a market as tokens are in the core of them. We started looking at some of these applications, in specific \textit{Bancor}~\cite{hertzog2017bancor}, to look into possible issues rising from these new models. Transparency of blockchains, although being a good feature of them, opens up these markets to some attack vectors that might not be visible on the time of the application design, one main attack is known as \textbf{front-running}, whether financial or non-financial. Arbitrage and Censorship, are also issues arises from the designs on the blockchain technology and had been linked to front-running attacks, hence we use the term \textit{front-running] losely to talk about any transaction manupulation with the intention of getting other transactions in before the original transaction takes place. In this paper, our focus is to have a complete overview of front-running on the blockchain while analysing Bancor issues. While looking at the possibility of front-running on other applications, we found interesting case studies that affects most of the top 25 decentral applications on Ethereum blockchain.

>>>>

The concept of the \emph{front-running} goes back to decades ago when financial instrument markets first started. Initially the traders required to be physically available in the exchange office to deliver the bids and offers, and some traders, in the knowledge of future market change, could run in front of the others to get their orders ahead of the change in the market to profit from the price change. Clearly in such scenarios front-running was possible yet not detectable as a damaging activity. However, with the rapid advances of the technology in the last few decades, trading is not carried out in person anymore and new form of front-running is feasible through high speed networks. Furthermore, Blockchain technology has introduced transparency and open markets and leads to a new era of front-running which inherently affects all decentral applications, whether financial or non-financial. Arbitrage and Censorship, are also issues that have been linked to front-running attacks on blockchain \textit{(We need to talk about why these two are left out of the scope of this paper)}. Currently, there are quite a few decentral applications built on the blockchains, so in order for us to perform a thorough study on blockchain application front-running, we set a s specific criteria by using the top 25 decentral applications which have the highest recent user activities.\footnote{List of decentralized applications \url{https://dappradar.com/dapps}} Using this criteria, we successfully categorized these decentral application s into 5 principal categories on which we conduct our analysis. Surprisingly, there was no ICO (initial coin offering) included in the top 25 Dapps list by the time we fetched the data from the website. We believe the reason is because the ICOs are inherently different from other groups of Dapss as they are merely highly active during their offering periods and their user activity drops dramatically after the offerings period are over. Therefore, we  consider ICOs as another cases on which the front-running should be investigated (although they are not listed in the top 25 Dapps we use) \footnote{A note to the reviewer: this paper falls under "Case Studies (\eg of adoption, attacks, forks, scams \etc)" and also mentions methods for "Fraud Detection and Financial Crime Prevention".}
